Texture mapping 3D planar models of indoor environments with noisy camera poses

### 2013-05-02 masters/body/newpaper.tex
masters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
Three-dimensional modeling of indoor environments has a variety of
applications in fields such as architecture and simulation. Adding
accurate textures to these models is important in adding context to
digital visualizations, and allows for image-based analysis of
environments.  In this paper, we work with a backpack-mounted system,
carried by an ambulatory human. This backpack system contains a series
of laser scanners and inertial measurement units, allowing it to solve
the simultaneous localization and mapping (SLAM) problem, which
produces backpack poses over time, and a point cloud representing its
environment. For our environment geometry, we work with models
obtained by fitting low-resolution planar surfaces to these point
clouds.  While a human-carried system provides advantages over more
common wheel-mounted systems in terms of agility and portability, it
often leads to relatively high localization error even after applying
sophisticated localization techniques. Furthermore, our model geometry
often contains some error as well, and is often adjusted to ignore
low-resolution features, such as small walls, furniture, and various
small features commonly found in indoor environments. As a result,
methods for texture mapping that rely on accurate camera poses
generally produce poor results.

Our goal of texturing planar surfaces with misaligned camera poses
straddles a number of highly-researched fields, including image
stitching, panorama generation, and image-based localization
algorithims. We will examine the results of existing approaches in
Section X, and compare them with our approach, which utilizes several
aspects of our modeling system and input data.

The remainder of the paper is organized as follows. Section X demonstrates 2 existing algorithms on our datasets and discusses unique aspects of our modeling system. Section X describes the basics of image projection, and a tile-based mapping approach and its shortcomings. Section X presents our approach towards image alignment, followed by Section X, which describes our two methods of compositing images. Section X contains results and conclusions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
Three-dimensional modeling of indoor environments has a variety of
applications in fields such as architecture, conservation, and
simulation. Applying accurate textures to these models is important in
adding context to digital visualizations, and allows for image-based
analysis of environments. In this paper, we perform data acquisition
with a backpack-mounted system carried by an ambulatory human. This
backpack system contains a series of laser scanners and inertial
measurement units, allowing it to solve the simultaneous localization
and mapping (SLAM) problem, which produces backpack poses over time as
well as a point cloud representing the surrounding environment. For
environment geometry, we work with models obtained by fitting
low-resolution planar surfaces to these point clouds.  While a
human-carried system provides advantages over more common
wheel-mounted systems in terms of agility and portability, it often
leads to relatively high localization error even after applying
sophisticated localization techniques. Furthermore, our model geometry
usually contains some error as well, and is often tuned to ignore
low-resolution features, such as small walls, furniture, and other
small non-planar features commonly found in indoor environments. As a
result, methods for texture mapping that rely on accurate camera poses
and projection surfaces generally produce poor results.

Our goal of texturing planar surfaces with misaligned camera poses
straddles a number of highly-researched fields, including image
stitching, panorama generation, and image-based localization
algorithims. We will examine the results of two existing approaches
from these fields of study in Section X, and compare them with our
approach, which utilizes several unique aspects of our modeling system
and input data.

The remainder of the paper is organized as follows. Section X
demonstrates 2 existing image stitching algorithms on our
datasets. Section X explains how images are projected onto our
geometry, and a simple approach towards texturing. Section X contains
our approach towards image alignment, followed by Section X, which
describes our two methods of compositing images. Section X contains
results and conclusions.

\section{Existing Approaches}
Stitching together multiple images to produce a larger image is a
commonly performed task, with many successful approaches over the past
years. Generally, parts of images are first matched to eachother,
usually through direct comparisons or feature detection and
matching. Images are then transformed to maximize matches, often by
calculating homographies between pairs of images, or by modifying
camera poses in 1 to 6 degrees of freedom.

Feature matching has a number of advantages over direct matching that
make it more suitable for our data, which is X. Feature matching
however, works best when multiple unique visual references exist in the
environment that can be detected in multiple images. In contrast, our
indoor environments have a high prevalence of bare surfaces, as well
as repeating textures that cause difficulty in disambiguating
features. This lack of reliable reference points often results in
errors when matching images together.

Additionally, our datasets often contain long chains of images, which
leads to error accumulation when image correspondences are not
exact. For example, when matching a long chain of images through
homographies, a pixel in the $nth$ image is translated into the first
image's coordinates by multiplying by the $3\times3$ matrices $H_1 H_2
H_3 ... H_n$. Errors in any of these homography matrices are
propagated to all further images, resulting in drift.

Past work with our data acquisition backpack integrated image
stitching with localization algorithms, and performed homography-based
alignment. As described above, this often resulted in drift, as shown in Figure X. This approach is also tied into a localization
algorithm, and its iterative camera adjustment process over our large
datasets leads to prohibitively long runtime.

Drift during image stitching can be combated using X. The AutoStitch software package
contains X. Though AutoStitch performs well in areas with dense
features, it can not handle even short segments of bare walls. The example in Figure X was generated after manual tuning, and areas with fewer visual
features or repeating texture patterns simply failed outright with AutoStitch.
